---
title: "Introduction to StatComp20027"
author: "WANG Yu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20027}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(comment = "#", warning = FALSE, eval = TRUE, message = FALSE)
set.seed(1)
library(StatComp20027)
```

## Overview
This package contains all my homework in the Statistical Computing course and two functions \code{d_mvnorm}, 
\code{r_mvnorm}

### functions
\code{r_norm} is a functions which can be used to generate multivariate normal distribution
random number. 

The source code is:

```{r, eval=FALSE}

# generate multivariate normal distribution
r_mvnorm <- function(n, mu, Sigma) {
    m = length(mu)
    mu.mat <- matrix(rep(mu, n), ncol=m, byrow=TRUE)
    # svd decomposition
    decop <- svd(Sigma)
    D <- decop$d
    dd <- diag(sqrt(D))
    
    # compute Sigma^(-1/2)
    A <- decop$u %*% dd %*% t(decop$v)
    u <- matrix(rnorm(m*n), ncol=m)
    # mr normal distribution random number
    rn <- u %*% A + mu.mat
    rn
}
```

\code{d_norm} is the probability density function of multivariate normal distribution.

The source code is:

```{r, eval=FALSE}

dmvnorm <- function(x, mu, Sigma) {
  n <- length(x)
  s <- -0.5 * ((x - mu) %*% solve(Sigma) %*% (x - mu))
  d.value <- 1/(sqrt(det(Sigma))*(pi^(n/2)))
  d.value*exp(s)
}
```
 \code{lck.reg} is a Nadariya-Watson estimator of the regression function.
 NW estimator constructs the regression model using local constant kernel method.
```{r, eval=FALSE}
rm(list=ls())

kernel <- function(x) {
    0.75*(1-x^2)*(abs(x)<1)
}
# Nadaraya-Watson estimator

lck.reg <- function(x, X, Y, h) {
    n <- length(x)
    result <- numeric(n)
    for (i in 1:n) {
        s <- kernel((x[i]-X)/h)
        result[i] <- s%*%Y / sum(s)
    }
    result
}

X <- runif(200, 0, 15)
Y <- (X-1.4)*(X-4.6)*(X-11.2) + rnorm(200, 0, 20)

```

